Forecasting the 2024 U.S. Presidential Election

### 2024-11-03 paper/paper.qmd
Delete the long table and finalize the paper.

```{r}
#| echo: false
#| tbl-cap: Complete Model Coefficient Summary Table
#| warning: false
#| message: false

# Get summary of the regression model
model_summary <- summary(regression_model)

# Extract and convert the coefficients summary to a data frame
coefficients_df <- as.data.frame(model_summary$coefficients)
colnames(coefficients_df) <- c("Estimate", "Std. Error", "t value", "Pr(>|t|)")

# Extract additional statistics
r_squared <- model_summary$r.squared
adj_r_squared <- model_summary$adj.r.squared
f_statistic <- model_summary$fstatistic[1]
p_value <- pf(f_statistic, model_summary$fstatistic[2], model_summary$fstatistic[3], lower.tail = FALSE)
residual_se <- model_summary$sigma

# Create a data frame for additional statistics with consistent column names and rounded to 2 decimals
additional_stats <- data.frame(
  Estimate = round(c(r_squared, adj_r_squared, f_statistic, p_value, residual_se), 2),
  `Std. Error` = NA,
  `t value` = NA,
  `Pr(>|t|)` = NA,
  row.names = c("R-squared", "Adjusted R-squared", "F-statistic", "F-statistic p-value", "Residual Std. Error")
)

# Ensure column names are identical between data frames
colnames(additional_stats) <- colnames(coefficients_df)

# Round coefficients to 2 decimal places in coefficients_df
coefficients_df <- coefficients_df %>%
  mutate(across(where(is.numeric), ~ round(., 2)))

# Combine the coefficients and additional statistics
full_summary_df <- rbind(coefficients_df, additional_stats)

# Display the full summary table using kable, excluding "F-statistic p-value" row
library(knitr)
kable(full_summary_df[!rownames(full_summary_df) %in% "F-statistic p-value", c("Estimate", "Std. Error", "t value")])

```
```{r, fig.width=10, fig.height=8}
#| echo: false
#| tbl-cap: Coefficient Estimates with 95% Confidence Intervals for Predictors. Predictors with positive coefficients are shown in blue, while predictors with negative coefficients are shown in red. 
#| warning: false
#| message: false

@@

# Plot the coefficients with confidence intervals, excluding the intercept
ggplot(tidy_model, aes(x = estimate, y = reorder(term, estimate))) +
  geom_point(aes(color = estimate > 0), size = 1.2) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), color = "grey", height = 0.3) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  scale_color_manual(
    values = c("red", "blue"),
    labels = c("Negative Coefficient", "Positive Coefficient"),
    name = ""  # This removes the default "estimate > 0" label
  ) +
  labs(x = "Coefficient Value", y = "Predictors") +
  theme_minimal(base_size = 14) +
  theme(
    axis.text.y = element_text(size = 10),
    axis.title.x = element_text(size = 14),
    axis.title.y = element_text(size = 14),
    plot.title = element_text(size = 16, face = "bold"),
    legend.position = "top"
  ) +
  guides(color = guide_legend(reverse = TRUE))

>>>>

```{r, fig.width=12, fig.height=10}
#| echo: false
#| tbl-cap: Coefficient Estimates with 95% Confidence Intervals for Predictors. Predictors with positive coefficients are shown in blue, while predictors with negative coefficients are shown in red. 
#| warning: false
#| message: false

@@

# Plot the coefficients with confidence intervals, excluding the intercept
ggplot(tidy_model, aes(x = estimate, y = reorder(term, estimate))) +
  geom_point(aes(color = estimate > 0), size = 1.2) +
  geom_errorbarh(aes(xmin = conf.low, xmax = conf.high), color = "grey", height = 0.3) +
  geom_vline(xintercept = 0, linetype = "dashed", color = "black") +
  scale_color_manual(
    values = c("red", "blue"),
    labels = c("Negative Coefficient", "Positive Coefficient"),
    name = ""  # This removes the default "estimate > 0" label
  ) +
  labs(x = "Coefficient Value", y = "Predictors") +
  theme_minimal(base_size = 16) +
  theme(
    axis.text.y = element_text(size = 12),
    axis.title.x = element_text(size = 16),
    axis.title.y = element_text(size = 16),
    plot.title = element_text(size = 16, face = "bold"),
    legend.position = "top", size= 20) +
  guides(color = guide_legend(reverse = TRUE))
